Child Signals of Need in Utila, Honduras: An Exploratory Study

### 2024-09-19 Paper.qmd
Removed some vars from summary table, and split table by sex

```{r sumtab_children}
#| label: tbl-sumtab_children
#| tbl-cap: Summary statistics for child study variables.
vars_c <- c(
  ChildAge = "Age (years)",
  SadFreqN = "Sad frequency (times per month)",
  CryFreqN = "Crying frequency (times per month)",
  TantrumFreqN = "Temper tantrum frequency (times per month)",
  AlloparentingFreqN = "Frequency of child's own alloparetning effort (times per month)",
  ConflictFreqN = "Frequency of conflict with focal caretaker (times per month)",
  SignalFreq = "Frequency of signals summed (times per month)",
  SignalCost = "Signal cost",
  SignalFreqMax = "Frequency of most common signal (times per month)",
  IllnessSusceptibility1 = "IllnessSusceptibility1",
  IllnessSusceptibility2 = "IllnessSusceptibility2",
  IllnessSusceptibility3 = "IllnessSusceptibility3",
  IllnessSusceptibilityMean = "Mean of current health measures",
  HeightZ = "Height Z-score (CDC)",
  WeightZ = "Weight Z-score (CDC)",
  BMIZ = "BMI Z-score (CDC)",
  SubscapMean = "Subscapular skinfold thickness (mm)",
  SubscapR = "Subscapular skinfold residuals",
  TricepMean = "Tricep skinfold thickness (mm)",
  TricepR = "Tricep skinfold residuals",
  BodyFat =  "Body fat composite"
)

kable(custom.summarize(modeldf, vars_c)) %>% kable_styling()

>>>>

```{r sumtab_children}
#| label: tbl-sumtab_children
#| tbl-cap: Summary statistics for child study variables.
vars_c <- c(
  ChildAge = "Age (years)",
  SadFreqN = "Sad frequency (times per month)",
  CryFreqN = "Crying frequency (times per month)",
  TantrumFreqN = "Temper tantrum frequency (times per month)",
  AlloparentingFreqN = "Frequency of child's own alloparetning effort (times per month)",
  ConflictFreqN = "Frequency of conflict with focal caretaker (times per month)",
  SignalFreq = "Frequency of signals summed (times per month)",
  SignalCost = "Signal cost",
  SignalFreqMax = "Frequency of most common signal (times per month)",
  # IllnessSusceptibility1 = "Illness Susceptibility1",
  # IllnessSusceptibility2 = "Illness Susceptibility2",
  # IllnessSusceptibility3 = "Illness Susceptibility3",
  IllnessSusceptibilityMean = "Illness avoidance index",
  HeightZ = "Height Z-score (CDC)",
  WeightZ = "Weight Z-score (CDC)",
  BMIZ = "BMI Z-score (CDC)",
  SubscapMean = "Subscapular skinfold thickness (mm)",
  SubscapR = "Subscapular skinfold residuals",
  TricepMean = "Tricep skinfold thickness (mm)",
  TricepR = "Tricep skinfold residuals",
  BodyFat =  "Body fat composite"
)

kable(custom.summarize(modeldf, vars_c, facvar = "Sex")) %>% kable_styling()
